Analyses

### 2021-11-05 analyses.RmD
- status when submitting first draft to ICA - reading entire paper for the first time

Filter waves without data

```{r eval=F}
d_long_test <- d_long %>%
  filter(!is.na(.[vars_varying]))
```

@@

Create vectors with names

```{r}
# create vector of names
vars_varying <- names(select(d_long, "health_b":"loc_cntrl_int_4_w"))
predictors_varying <- select(d_long, "health_b":"loc_cntrl_int_4_w") %>% 
  select(-starts_with("aff_"), -starts_with("life_")) %>% 
  names()
```

# inspect data

@@

# measures
## well-being
### life satisfaction

@@

### positive affect

@@

### negative affect

@@

## Social media use
### reading

@@

### liking & sharing

@@

### posting

@@

## figure

@@

## table

```{r}
tab_desc_dat <- rbind(
    "Life satisfaction" = get_specs(model_life_sat),
    "Positive affect" = get_specs(model_aff_pos),
    "Negative affect" = get_specs(model_aff_neg),
    "Read" = get_specs(model_soc_med_read),
    "Like & share" = get_specs(model_soc_med_like_share),
    "Posting" = get_specs(model_soc_med_post),
    "Facebook" = get_specs(model_soc_med_fb),
    "Twitter" = c(sd = get_specs(model_soc_med_tw)$sd,
                  min = min(soc_med_tw_m$value, na.rm = TRUE),
                  max = max(soc_med_tw_m$value, na.rm = TRUE),
                  mean = mean(soc_med_tw_m$value, na.rm = TRUE)
                  ),
    "Instagram" = get_specs(model_soc_med_ig),
    "WhatsApp" = get_specs(model_soc_med_wa),
    "YouTube" = get_specs(model_soc_med_yt)
    )
```

# analyses
## life satisfaction

@@

```{r}
# + health_b + act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b + sat_dem_b + hh_income_b + med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + med_vid_orf_b + med_vid_pri_b + risk_prop_b + loc_cntrl_int_1_b + loc_cntrl_int_2_b + loc_cntrl_int_3_b + loc_cntrl_int_4_b + health_w + act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + sat_dem_w + hh_income_w + med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + med_vid_orf_w + med_vid_pri_w + risk_prop_w + loc_cntrl_int_1_w + loc_cntrl_int_2_w + loc_cntrl_int_3_w + loc_cntrl_int_4_w
```

@@

```{r}
# get data
dat_fig_results <- 
  broom.mixed::tidy(model_aff_neg_lmer, conf.int = T) %>% 
  mutate(dv = "aff_neg") %>% 
  rbind(
    broom.mixed::tidy(model_aff_pos_lmer, conf.int = T) %>% 
    mutate(dv = "aff_pos")
  ) %>% 
  rbind(
    broom.mixed::tidy(model_life_sat_lmer, conf.int = T) %>% 
    mutate(dv = "life_sat")
  ) %>% 
  mutate(
    type = ifelse(grepl(".*_w.*", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    type = factor(.$type, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect"))
  ) %>% 
  select(dv, iv, type, estimate, conf.low, conf.high, p.value)
```

@@

# make figure
fig_results_activity <- make_graph_res(dat_fig_results_activity)

@@

# make figure
fig_results_channel <- make_graph_res(dat_fig_results_channel)

@@

# make figure
fig_results_control <- make_graph_res(dat_fig_results_control, sesoi = FALSE)

>>>>

<!-- Filter waves without data -->

<!-- ```{r eval=F} -->
<!-- d_long_test <- d_long %>% -->
<!--   filter(!is.na(.[vars_varying])) -->
<!-- ``` -->

@@

<!-- Create vectors with names -->

<!-- ```{r} -->
<!-- # create vector of names -->
<!-- vars_varying <- names(select(d_long, "health_b":"loc_cntrl_int_4_w")) -->
<!-- predictors_varying <- select(d_long, "health_b":"loc_cntrl_int_4_w") %>%  -->
<!--   select(-starts_with("aff_"), -starts_with("life_")) %>%  -->
<!--   names() -->
<!-- ``` -->

# Inspect data

@@

# Measures
## Well-being
### Life satisfaction

@@

### Positive affect

@@

### Negative affect

@@

## Social media use
### Reading

@@

### Liking & sharing

@@

### Posting

@@

## Figure

@@

## Table

```{r}
tab_desc_dat <- rbind(
    "Life satisfaction" = get_specs(model_life_sat),
    "Positive affect" = get_specs(model_aff_pos),
    "Negative affect" = get_specs(model_aff_neg),
    "Read" = get_specs(model_soc_med_read),
    "Like & share" = get_specs(model_soc_med_like_share),
    "Posting" = get_specs(model_soc_med_post),
    "Facebook" = get_specs(model_soc_med_fb),
    "Twitter" = c(sd = get_specs(model_soc_med_tw)$sd,
                  min = min(soc_med_tw_m$value, na.rm = TRUE),
                  max = max(soc_med_tw_m$value, na.rm = TRUE),
                  mean = mean(soc_med_tw_m$value, na.rm = TRUE)
                  ),
    "Instagram" = get_specs(model_soc_med_ig),
    "WhatsApp" = get_specs(model_soc_med_wa),
    "YouTube" = get_specs(model_soc_med_yt)
    )
kable(tab_desc_dat)
```

# Analyses
## Life satisfaction

@@

@@

```{r}
# get data
dat_fig_results <- 
  broom.mixed::tidy(model_aff_neg_lmer, conf.int = T) %>% 
  mutate(dv = "aff_neg") %>% 
  rbind(
    broom.mixed::tidy(model_aff_pos_lmer, conf.int = T) %>% 
    mutate(dv = "aff_pos")
  ) %>% 
  rbind(
    broom.mixed::tidy(model_life_sat_lmer, conf.int = T) %>% 
    mutate(dv = "life_sat")
  ) %>% 
  mutate(
    type = ifelse(grepl(".*_w\\>", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    type = factor(.$type, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect"))
  ) %>% 
  select(dv, iv, type, estimate, conf.low, conf.high, p.value)
```

@@

# make figure
fig_results_activity <- make_graph_res(dat_fig_results_activity)
fig_results_activity

@@

# make figure
fig_results_channel <- make_graph_res(dat_fig_results_channel)
fig_results_channel

@@

# make figure
fig_results_control <- make_graph_res(dat_fig_results_control, sesoi = FALSE)
fig_results_control
